Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-07-11 paper.tex
edit the table
Update paper.tex

\gmj{Li, are you familiar with the analytical tools MIGRATE-N and BAYESASS?  Rieseberg comapres these two to STRUCTURE at some length in the discussion of this paper:
https://biology.unm.edu/Whitney/Whitney%20Reprints/Scascitelli%20et%20al%202010.pdf
Should we include these two methods, even in passing, in this portion of the paper?}

@@

\rowcolor{white}
{\emph{\bf population structure related}} &   &   &   \\
\rowcolor{white}
fineStructure &	phased haplotype &	Lawson et al. 2012	& Skoglund et al. 2015 \\
\rowcolor{white}
Globetrotter &	phased haplotype &	Hellenthal et al. 2014 & Scott et al. 2016 \\
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{vertical.png}
	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature.}
	\label{boxplot:map}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{boxplot_3.png}
	\caption{The distribution of average annual temperature experienced in the geographic home ranges of wild relatives interfertile with four crops}
	\label{fig:map}
\end{figure}

>>>>

\gmj{Li, are you familiar with the analytical tools MIGRATE-N and BAYESASS?  Rieseberg comapres these two to STRUCTURE at some length in the discussion of this paper:
https://biology.unm.edu/Whitney/Whitney%20Reprints/Scascitelli%20et%20al%202010.pdf
Should we include these two methods, even in passing, in this portion of the paper?}
\lwang{Garrett, I donot know these two methods. I am reading the paper you mentioned here.}

@@

\end{tabular}
\end{center}
\end{table}

@@

%\begin{figure}[h]
%	\centering
%	\includegraphics[width=17.35cm]{vertical.png}
%	\caption{Map of the natural ranges of wild relatives of four domesticated crops, overlayed with average annual temperature.}
%	\label{boxplot:map}
%\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=17.35cm]{combination.png}
	\caption{Map of the natural ranges of wild relatives of three domesticated crops, overlayed with average annual temperature. The distribution of average annual temperature experienced in the geographic home ranges of wild relatives interfertile with four crops}
	\label{fig:map}
\end{figure}
